Between Subgraph Isomorphism and Maximum Common Subgraph

### 2016-09-13 paper/paper.tex
emphasising.

By an assignment, we mean considering mapping a pattern vertex $p$ to a target vertex $t$ (and not
$\bot$) which does not violate any loop constraints. An assignment pair is two assignments with
distinct $p$ and distinct $t$, which we say is permitted if it does not violate any adjacency
constraint. We define the permitted assignment pair ratio to be the proportion of assignment pairs
which are permitted.  Finally, in \cref{figure:constraints} we scatter plot the permitted assignment
pair ratio with and without supplemental graphs\footnote{Because of the large sizes of the domains,
we randomly sample one million pairs rather than considering every pair. In some cases, we have
nearly a thousand domains, each with nearly ten thousand values---a complete quadratic calculation
involving even a trivial arithmetic operation on this would take many hours.}.

>>>>

By an \emph{assignment}, we mean considering mapping a pattern vertex $p$ to a target vertex $t$ (and not
$\bot$) which does not violate any loop constraints. An \emph{assignment pair} is two assignments with
distinct $p$ and distinct $t$, which we say is permitted if it does not violate any adjacency
constraint. We define the \emph{permitted assignment pair ratio} to be the proportion of assignment pairs
which are permitted.  Given this, in \cref{figure:constraints} we scatter plot the permitted assignment
pair ratio with and without supplemental graphs\footnote{Because of the large sizes of the domains,
we randomly sample one million pairs rather than considering every pair. In some cases, we have
nearly a thousand domains, each with nearly ten thousand values---a complete quadratic calculation
involving even a trivial arithmetic operation on this would take many hours.}.
